\textcolor{violet}{Reverse Correlation Uncovers More Complete Tinnitus Spectra \vspace{0.25cm}}

### 2023-01-05 paper/short/main_wc995.tex
Final Review

\author{Alec Hoyland, Nelson V. Barnett, Benjamin W. Roop, Danae Alexandrou, Myah Caplan, Jacob Mills, Benjamin Parrell, Divya A. Chari, and Adam C. Lammert\textsuperscript{\textdagger{}}%
\thanks{This work was supported in part by the University of Massachusetts
Center for Clinical and Translation Science.}%
\thanks{A. Hoyland is with the Department of Biomedical Engineering (BME)
at Worcester Polytechnic Institute (WPI), Worcester, MA and with Clarifai, Inc., Wilmington, DE.
N.V. Barnett, M. Caplan, J. Mills and A.C. Lammert are also with BME at WPI.
B.W. Roop is formerly of the Neuroscience Program at WPI.
D. Alexandrou is with the Stritch School of Medicine at Loyola University Chicago, Chicago, IL.
B. Parrell is with the Department of Communication Sciences and Disorders and the Waisman Center at University of Wisconsin, Madison, WI. D.A. Chari is with the
University of Massachusetts Chan Medical School, Worcester, MA
and the Massachusetts Eye and Ear Infirmary,
Boston, MA.
The authors declare no competing interests.}%
\thanks{\textsuperscript{\textdagger{}} Corresponding Author}}%

@@

% INTRO PARAGRAPH 2/3
Nontonal tinnitus sounds are presumed to be complex and heterogeneous
\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,henryTinnitusEpidemiologicPerspective2020},
although few characteristics have been firmly established.
Therefore, we base our approach on \textit{reverse correlation} (RC),
an established behavioral method
\cite{ahumadaStimulusFeaturesSignal1971,gosselinSuperstitiousPerceptionsReveal2003,brimijoinInternalRepresentationVowel2013}
for estimating internal perceptual representations that is unconstrained by prior knowledge about the representations themselves.
RC asks subjects to render subjective judgments over random stimuli, being closely related to Wiener theory,
which has inspired ``white-noise'' approaches to system characterization in physiology
\cite{ringachReverseCorrelationNeurophysiology2004,marmarelisWhiteNoiseMethodSystem1978} and engineering \cite{ljungMeasureLackFit1978}.

@@

% NB NOTE: What is s?? ACL: it is the target sound vector
for $i \in 1, ..., p$, where $Q(x, y)$ is the quantile function for $x \in [0, 1]$ of the similarity calculation $\Psi s$, and
$\Psi_i$ is the $i^\mathrm{th}$ column of $\Psi$.
Thus, the ideal subject has precise knowledge of every stimulus and responds according to Eq. \ref{eq:subjresp}. The \textit{random} subject responds $y_i \in \{1,-1\}^n$ with uniform random probability, thus ignoring the stimulus entirely.

>>>>

\author{Alec Hoyland, Nelson V. Barnett, Benjamin W. Roop, Danae Alexandrou, Myah Caplan, Jacob Mills, Benjamin Parrell, Divya A. Chari, and Adam C. Lammert\textsuperscript{\textdagger{}}%
\thanks{This work was supported in part by the University of Massachusetts
Center for Clinical and Translation Science.}%
\thanks{A. Hoyland is with the Department of Biomedical Engineering (BME)
at Worcester Polytechnic Institute (WPI), Worcester, MA and with Clarifai, Inc., Wilmington, DE.
N.V. Barnett, M. Caplan, J. Mills and A.C. Lammert are also with BME at WPI.
B.W. Roop is of the Neuroscience Program at WPI.
D. Alexandrou is with the Stritch School of Medicine at Loyola University Chicago, Chicago, IL.
B. Parrell is with the Department of Communication Sciences and Disorders and the Waisman Center at University of Wisconsin, Madison, WI. D.A. Chari is with the
University of Massachusetts Chan Medical School, Worcester, MA
and the Massachusetts Eye and Ear Infirmary,
Boston, MA.
The authors declare no competing interests.}%
\thanks{\textsuperscript{\textdagger{}} Corresponding Author}}%

@@

% INTRO PARAGRAPH 2/3
Nontonal tinnitus sounds are presumed to be complex and heterogeneous
\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021},
although few characteristics have been firmly established.
Therefore, we base our approach on \textit{reverse correlation} (RC),
an established behavioral method
\cite{ahumadaStimulusFeaturesSignal1971,gosselinSuperstitiousPerceptionsReveal2003,brimijoinInternalRepresentationVowel2013}
for estimating internal perceptual representations that is unconstrained by prior knowledge about the representations themselves.
RC asks subjects to render subjective judgments over random stimuli, being closely related to Wiener theory,
which has inspired ``white-noise'' approaches to system characterization in physiology
\cite{ringachReverseCorrelationNeurophysiology2004,marmarelisWhiteNoiseMethodSystem1978} and engineering \cite{ljungMeasureLackFit1978}.

@@

% NB NOTE: What is s?? ACL: it is the target sound vector
for $i \in 1, ..., p$, where $Q(x, y)$ is the quantile function for $x \in [0, 1]$ of the similarity calculation $\Psi s$, and
$\Psi_i$ is the $i^\mathrm{th}$ column of $\Psi$.
Thus, the ideal subject has precise knowledge of every stimulus and responds according to Eq. \ref{eq:subjresp}. The \textit{random} subject responds $y_i \in \{1,-1\}$ with uniform random probability, thus ignoring the stimulus entirely.
